{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
specified which state
corrected typo

At this point a first simplification can be made. Looking a state $s$ we can
first extract the active threads (\texttt{s.act}) by taking the domain of the first
component. According to a security environment we can classify these threads,
with respect to their current program point (\texttt{s.pc(tid)} where $tid \in Thread$),
into \textit{low} threads iff the current program point is low. In \textit{high}
threads iff the current program point is high. In \textit{always high} threads
iff the current program point is always high and in \textit{hidden} threads, iff
the current program point is high but not always high.

The latte two are the interesting ones. If a thread is \textit{always high} it
can not leaks any information into low, because it never only gets in touch
with low program points. So these threads can safely be interleaved by the
scheduler.

>>>>

At this point a first simplification can be made. Looking a state $s \in ConcState$ we can
first extract the active threads (\texttt{s.act}) by taking the domain of the first
component. According to a security environment we can classify these threads,
with respect to their current program point (\texttt{s.pc(tid)} where $tid \in Thread$),
into \textit{low} threads iff the current program point is low. In \textit{high}
threads iff the current program point is high. In \textit{always high} threads
iff the current program point is always high and in \textit{hidden} threads, iff
the current program point is high but not always high.

The latter two are the interesting ones. If a thread is \textit{always high} it
can not leaks any information into low, because it never only gets in touch
with low program points. So these threads can safely be interleaved by the
scheduler.
